\documentclass[11pt]{article}
\usepackage{standalone} \newif\ifstandlone \standalonetrue
\usepackage[left=1.75in, right=1.75in, top=1.25in, bottom=1.25in]{geometry}
\geometry{letterpaper}
\usepackage{graphicx}
\usepackage{enumitem}
%\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{epstopdf}
\usepackage{setspace}
\usepackage{natbib}
\setcitestyle{aysep={}}
\usepackage{hyperref}
		
\synctex=1

\DeclareSymbolFont{symbolsC}{U}{txsyc}{m}{n}
\DeclareMathSymbol{\strictif}{\mathrel}{symbolsC}{74}
\DeclareMathSymbol{\boxright}{\mathrel}{symbolsC}{128}

\newenvironment{squote}{%
	\begin{quote}\begin{singlespace}%
	}{%
	\end{singlespace}\end{quote}}

\newcommand{\stager}[4]%
{%
	\begin{spacing}{1}%
	\vspace{0pt}
		\begin{description}[style=nextline, noitemsep,
                    parsep=0pt, topsep=0pt, leftmargin=15mm,
                    itemindent=-10mm, font=\mdseries]
			\item[\textsc{#1} \emph{#2}] #3
			\item[]%
			\begin{flushright}#4\end{flushright}
		\end{description}%
	\end{spacing}%
}

\newcommand{\stage}[3]%
{%
	\begin{spacing}{1}%
	\vspace{0pt}
		\begin{description}[style=nextline, parsep=0pt,
                    leftmargin=15mm, itemindent=-10mm, font=\mdseries]
			\item[\textsc{#1} \emph{#2}] #3
		\end{description}%
	\end{spacing}%
}

\newenvironment{inq}{\vspace{0pt}%
	\begin{list}{}%
	{\setlength\labelwidth{0pt}%
	\setlength\leftmargin{2.5\oddsidemargin}%
	\setlength\rightmargin{\leftmargin}}
	\begin{spacing}{1}
	\item[]%
	}{
	\end{spacing}
	\end{list}
	\vspace{10pt}
	%\noindent%
	}

\title{Unger's arguments}
\author{Alex Dunn}
\begin{document}
\ifstandalone
\maketitle
\begin{spacing}{1.5}
\fi

Peter Unger has presented several arguments that threaten the kind of
universalism I sketched in section \ref{universalism}.  The versions
of the sorites paradox that he presents make trouble for all vague
concepts, including those that Merricks relies on for his version of
nihilism.  Unger's `problem of the many', on the other hand, poses a
problem specifically for universalism.

\section{Incoherence and pluralities}
\label{unger}
Like Peter van Inwagen and Trenton Merricks, Peter Unger has denied
the existence of all `ordinary things'---such things as ``tables and
chairs and spears\,\ldots swizzle sticks and
sousaphones\,\ldots\,stones and rocks and twigs, and also tumbleweeds
and fingernails'' (\citeyear[117]{unger1979}).  Merricks has a
different motivation for his nihilism than does van Inwagen, and Unger
has a different motivation again.  In fact, he has two different
motivations; one is the sorites paradox and the other is the problem
of the many.  

Unger claims that the sorites paradox shows that terms for ordinary
things, like `chair', are {\em incoherent}.  He claims that incoherent
terms cannot apply to anything in the world; therefore he concludes
that there are no chairs (or any other ordinary thing).

Unger's presentation of the problem of the many is aimed to trouble
the concept of `chair' in a different way.  The conclusion of that
argument is not that `chair' is necessarily incoherent.  Rather, the
conclusion is a disjunction: {\em either} there are no chairs, {\em
  or} there are a plurality (possibly an infinity) of chairs where we
would normally take there to be only one.

We will examine these two arguments in turn.

\section{Sorites paradoxes}
\label{sorites}
A typical instance of the sorites paradox begins by having us imagine
some ordinary object; let us use a heap of sand.  Now suppose we
remove a single grain of sand.  If we were inclined to believe that
the initial quantity of sand did in fact constitute a heap, then after
the removal of a single grain, we should presumably still have a heap
(albeit a slightly smaller one).  It seems very implausible to think
that one grain of sand more or less could {\em ever} make a difference
as to whether something is or is not a heap.

But having conceded (a) that there is a heap and (b) that the removal
of a single grain cannot make the difference as to whether a quantity
of sand is a heap, we have unwittingly put our foot in it.  For if the
removal of a single grain {\em never} transforms a heap into a
non-heap, then by repeatedly removing one grain after another, we will
eventually find ourselves with a heap that consists of no sand at
all.  But it seems absurd to suppose that there could be a heap of
sand that is composed of no sand---indeed, of nothing whatsoever.

This is the sorites paradox.  While a heap is a useful example,
because it is so ill-defined, similar problems appear to afflict all
ordinary things.  Unger illustrates the difficulty for stones:

\begin{squote}
Consider a stone, consisting of a certain finite number of atoms.  If
we or some physical process should remove one atom, without
replacement, then there is left that number minus one, presumably
constituting a stone still\,\ldots after another atom is removed,
there is that original number minus two; so far, so good.  But after
that certain number has been removed, in similar stepwise fashion,
there are no atoms at all in the situation, while we must still be
supposing that there is a stone there.  But as we have already agreed,
if there is a stone present, then there must be some atoms\,\ldots I
suggest that any adequate response to this contradiction must
include\,\ldots the denial of the existence of even a single
stone.~\citep[121--122]{unger1979}
\end{squote}
Unger understands this dilemma to apply across the board, and
correspondingly argues that we should deny the existence of even a
single ordinary thing.

\subsection{The sorites paradox in relation to Merricks' nihilism}
\label{sorites-m}
The purpose of Unger's argument is to show that terms that are
susceptible to the sorites paradox are incoherent and cannot apply to
anything in the world.  Unger claims that terms like `chair' therefore
cannot apply to anything in the world---from which it follows that
there are no chairs.

Trenton Merricks' version of nihilism (section \ref{merricks}) denies
that there are chairs.  In this, Merricks is in agreement with Unger.
But unlike Unger, Merricks maintains that beliefs like ``there are
chairs'' are {\em justified} and {\em nearly as good as true}.  He
claims that such beliefs are nearly as good as true if they are caused
by simples arranged chairwise.  Merricks does not believe that there
are chairs, so ``there are chairs'' is, strictly speaking, false.  But
Merricks believes that there are simples arranged chairwise, and the
presence of such arrangements cause and justify false beliefs such as
``there are chairs''.

We have seen, however, that the sorites paradox threatens the
coherency of concepts like `chair'.  If we suppose that a given
collection of atoms composes a chair, we can remove them one by one
and at no point feel justified in saying that the chair suddenly
ceases to exist.  Now suppose that a given arrangement of simples is
arranged chairwise.  Remove one.  Is the arrangement still arranged
chairwise?  Just as in the case of the chair, it seems bizarre to
think that a single simple (or atom) can make a difference as to
whether `chairwise' applies.  But now remove another atom\,\ldots

If Unger's argument shows that the concept of `chair' is incoherent,
then it seems that the same argument shows the concept of `chairwise'
to be incoherent.  If so, then `chairwise' can apply to nothing in the
world.  There can be no chairwise arrangements of simples.  If there
are no chairwise arrangements of simples, then our belief that there
are chairs cannot be nearly as good as true.  If someone believes that
there is a ghost, that belief, according to Merricks, is not nearly as
good as true because there are no ghostwise arrangements of simples to
cause or justify the belief that there is a ghost.  If `chairwise' is
incoherent, then there are no chairwise arrangements of simples to
cause or justify the belief that there are chairs.  The belief that
there are chairs is (if Unger is right) simply false, just as is the
belief that there are ghosts.

Merricks cannot allow this conclusion.  But the sorites paradox can be
used to show that {\em any} vague term is incoherent.  Much of our
language is vague, but we are not therefore tempted to conclude that
our speech is rarely (if ever) coherent.  The problem of the sorites
paradox is a very general problem that requires a general theory of
vagueness.  Most metaphysical theories are threatened by the sorites
paradox; Merricks is not a special case.

With that in mind, it should not be surprising that Merricks does not
have full answer.  A full answer to the sorites paradox would be a
theory of vagueness.  Merricks is not trying to establish a theory of
vagueness, but it attempting to motivate a metaphysical thesis about
ordinary things.  That said, he does have a {\em partial} answer.  He
points out that while the sorites paradox does threaten the concept of
`chairwise', it does so in a less troubling way than the way in which
it threatens `chair'.  

How is the sorites paradox ``less troubling'' for chairwise
arrangements than for chairs?  Very roughly, it is because accepting
the vagueness of `chair' can lead us to {\em metaphysical} vagueness,
while accepting the vagueness of `chairwise' can only lead us to {\em
  linguistic} vagueness.  And linguistic vagueness is generally
considered to be less troubling than metaphysical vagueness.

We can get a sense of how this is so by imagining, as Merricks does,
the sorites paradox being played out as a series of questions.  Let us
suppose that there is a chair.  We then ask ourselves (Merricks asks
God), ``is `there is a chair' true?''  Presumably we will answer
``yes''.  Then we remove one atom (or simple, or other thing) from the
chair.  ``Is `there is a chair' true?''

If we agree that there is no single atom whose removal would destroy
the chair, then we must accept that at some point it becomes
indeterminate whether ``there is a chair'' is true.  If it is
indeterminate whether ``there is a chair'' is true, then it is
indeterminate whether there is a chair.  The idea that it could be
indeterminate whether something exists is taken by many to be
problematic (\textbf{CITE}).

We can compare this case with that of the things arranged chairwise.
Let us suppose that there are things arranged chairwise.  We ask ``is
`there things arranged chairwise' true?'' and answer ``yes''.  Then we
remove a thing and ask ``is `there things arranged chairwise' true?''
As in the chair case, if we are unwilling to allow that the removal of
a single thing could take us from ``yes'' to ``no'', then we must
admit that at some point it is indeterminate whether or not ``there
are things arranged chairwise'' is true.  It would then be
indeterminate whether there are things arranged chairwise.  {\em But
  this does have the result that it is indeterminate whether something
  exists.}  It may be perfectly determinate that there are the things
there are; all that is indeterminate is whether the things (which
there determinately are) are arranged in a certain way.  This kind of
indeterminacy seems less troubling than indeterminacy as to whether
something (a chair or anything else) exists.

Merricks therefore sees the problem posed by the sorites paradox as
less threatening to his chairwise arrangements than to chairs.  He
does not attempt to provide a solution, for that would require solving
the problem of linguistic vagueness.  But he finds the problem of
linguistic vagueness less troubling than the problem of metaphysical
vagueness, and he shows that the latter does not threaten his version
of nihilism.

\subsection{So what's the problem?}
\label{sorites-3}
We find ourselves wanting to hold three theses, which appear mutually
inconsistent:

\begin{enumerate}
  \item There is at least one chair (stone, cloud).
  \item If a chair (stone, cloud) exists, it must be made up of
    matter.
  \item If a chair (stone, cloud), exists, the removal of a single
    molecule (or otherwise insignificant quantity of matter) from it
    cannot destroy it or cause it to cease to exist.
\end{enumerate}

We seem to be clearly caught in a paradox; the only question is where
we have gone wrong.

But have we, in fact, gone wrong?  Peter Unger thinks that we are
right on target:

\begin{squote}
While Eubulides' contribution has often been labeled `the sorites
paradox', there is nothing here which is a paradox in any
philosophically important sense\,\ldots Accepting our negative
conclusions here does not mean important logical trouble for us; we
only think we have troubles while we refuse to admit their validity
(\citeyear[145]{unger1979}).
\end{squote}

Our situation is only paradoxical, says Unger, while we unreflectingly
cling to the first thesis.  If, however, we come to see that there are
no chairs (stones, clouds), then we happily escape paradox: if there
are no chairs (stones, clouds) to begin with, we do not have to worry
about what the addition or removal of small amounts of matter would do
to them; nor do we need concern ourselves with what they would be made
of.

But things are not quite so simple.  First, adding to the
implausibility of Unger's view, he must deny that our use of ordinary
terms like `chair' (`stone', `cloud') follow any sort of pattern or
display any competence at all.  Second, even if we manage to swallow
that consequence, Unger has no explanation as to why we believe that
there are chairs (stones, clouds).

\subsection{Competence and correctness}
\label{correct}
Setting aside whether or not expressions of propositions like ``that's
a chair'' are ever \emph{true}, it seems right to say that there are
at least correct and incorrect uses of the terms.  For a word like
`chair' (`stone', `cloud') we generally do not say that a child has
learned how to use it until she is capable of deploying it in certain
ways.  We admit that she understands what `chair' (`stone', `cloud')
means or what a chair (stone, cloud) is when she displays a certain
competence with the term.  If instead of using `chair' to refer to
chairs she used it to refer to dogs or people, we would say that she
is confused and attempt to correct her use.

But Unger maintains that this is all an illusion, and that there is no
such thing as the correct or incorrect use of a term like `chair'
(`stone', `cloud'):

\begin{squote}
Concerning words and kinds, now, we might say this.  First, we might
say that it is in connection with \emph{semantics} that our reasonings have
what are their most obvious implications and, second, that their most
obvious semantic implications concern certain \emph{sortal nouns}, namely,
those which purport to denote ordinary things.  Thus, it appears quite
obvious to us now that there will be no application to things for such
nouns as `stone' and `rock', `twig' and `log', `planet' and `sun',
`mountain' and `lake', `sweater' and `cardigan', `telescope' and
`microscope', and so on, and so forth.  Simple positive sentences
containing these terms will never, given their current meanings,
express anything true, correct, accurate, etc., or even anything which
is anywhere close to being any of those things
(\citeyear[148]{unger1979}).
\end{squote}

This seems simply bizarre.  On what grounds, then, do parents correct
their children with respect to their use of ordinary terms?  Are they
compelled by some irrational force to consider certain utterances
correct and others incorrect?  One may question whether or not we use
ordinary term entirely consistently, but it seems simply false to say that,
necessarily, we {\em never} use (or have used, or will use) ordinary
terms in correct, as opposed to incorrect, ways.  

The fact that Unger's position means that terms like `chair' are never
used correctly gives us reason to think his argument goes awry
somewhere.  However, attempting to identify the issue with his
argument and proposing a solution would be tantamount to attempting to
solve the problem of vagueness.  That is not something I will attempt,
at least not until we have examined the problem of the many.

\section{The problem of the many}
\label{many}
The `problem of the many', as Unger terms this second difficulty for
ordinary things, follows a similar line of reasoning as that of the
sorites paradox.  If we consider an ordinary thing---a cloud, for
instance---it is natural to think that it is made up of molecules.
There is probably then a set of molecules, the members of which make
up the cloud.  Call that set $S$.  Now consider $S_1$.  This is a set
of molecules that includes all of the members of $S$ as well as one
additional molecule.  Do the members of $S_1$ make up a cloud?  Surely
they are just as well suited to do so.  Now consider $S_2$\,\ldots

Because these numerous 'candidates' are equally (or nearly equally)
well suited to be clouds, we seem forced to conclude that there are
either many clouds where we supposed there to be one, or rather no
clouds at all:

\begin{squote}
No matter where we start, the complex first chosen has nothing
objectively in its favor to make it a better candidate for cloudhood
than so many of its overlappers are.  Putting the matter somewhat
personally, each one's claim to be a cloud is just as good, no better
and no worse, than each of the many others.  And, by all odds, each
complex has \emph{at least} as good a claim as any still further real
entity in the situation.  So, either \emph{all} of \emph{them} make it
or else \emph{nothing} does; in this real situation, either there are
many clouds or else there really are no clouds at all
\citep[415]{unger1980a}.
\end{squote}

The problem of the many can also arise by considering the {\em
  boundary} of a given cloud.  It is natural to suppose that a cloud
has a determinate boundary.  But if we look at the edge of the cloud,
where we suppose the boundary to be, ``we may find, side by side, or
themselves overlapping, a great many potential boundaries for
clouds\,\ldots if our alleged typical item {[}the cloud{]} is indeed
a typical cloud, then many of these candidates, millions at least, do
not fail to be clouds altogether but are clouds of some
sort'' \citep[420--421]{unger1980a}.

The pattern of argumentation is the same for both approaches to the
problem of the many.  For a given cloud, a certain set of members or a
certain boundary is supposed, and it is argued that a set or boundary
that differs minimally from the original must also make up or bound a
cloud.  The new set or boundary does not appear to differ from the
original in any relevant way; there seems no principled reason to deny
that if the first set's members make up a cloud, the second set's
members do too.  And since there are a great deal of very similar sets
and boundaries, we find ourselves threatened with a plurality of
clouds.

And of course, Unger does not rest content with applying the problem
of the many to clouds.  All ordinary objects get the same treatment;
he concludes that either there are a great many of them, or there are
none at all.  He claims, predictably, that the latter disjunct is
preferable.

\subsection{Is the problem of the many a problem for Merricks?}
\label{many-merricks}
It might seem that the problem of the many, if it makes things
difficult for chairs and other ordinary things, also causes trouble
for the chairwise arrangements upon which Merricks relies so heavily.
But there is an important disanalogy.  The problem of the many is only
a problem as long as we are unwilling to accept one of Unger's
disjuncts: that there are no chairs or that there are a plurality
where we took there to be one.  Whether or not it is part of the
meaning of `chair' that there is not an overlapping plurality of
chairs, it is simply unacceptable that this be the case.  (It is
likewise unacceptable that there be no chairs.)  But it {\em is}
acceptable, at least initially, that there be a plurality of chairwise
arrangements.  The idea that there is a plurality of different sets,
the members of which overlap and of which all are arranged chairwise,
is not particularly bizarre.  A potential difficulty for Merricks
would be in regard to his criterion of `arranged chairwise' (or
statuewise, as the case may be):

\begin{squote}
Atoms are \emph{arranged statuewise} if and only if they both have the
properties and also stand in the relations to microscopica upon which,
if statues existed, those atoms' \emph{composing a statue} would
non-trivially supervene (\citeyear[4]{merricks2001a}).
\end{squote}

If Merricks allows that there may be a plurality of statuewise
arrangements, then he is committed to the proposition that, if statues
existed, there may be pluralities of statues.  But Merricks may simply
take this as more evidence that his counterpossible conditional (``if
there were statues\,\ldots '') really is impossible.

There may be, however, a problem for Merricks with regard to the
notion of `singular thought'.  If Merricks says to me, ``those things
arranged chairwise are arranged very comfortably'', how can I know
which things he is talking about?  If there are numerous different
sets of things arranged chairwise, the chance that I am thinking of
the same things as Merricks is very low.  Are we really communicating,
then?  (Moreover, is it true that I am thinking of {\em any}
determinate set of things?  I certainly couldn't specify which
particular things I am thinking of.)

If the problem of the many is a problem for Merricks, then so much the
worse for his nihilism.  However, the problem is a problem for us as
well.

\section{Beliefs in things}
\label{u-belief}
When we examined previous versions of nihilism, we asked that their
proponents explained why, if there are no chairs, we nonetheless
believe that there are chairs.  Van Inwagen and Merricks both made a
claim to the effect that our beliefs are caused and (in some sense)
justified by arrangements of simples.  Although Merricks denies that
beliefs like ``there is a fine chair'' are strictly true, he agrees
with van Inwagen that they `get something right' in a way that beliefs
like ``there is a dancing chair'' do not.  Their explanation for our
belief that there are chairs is that they are caused (and justified)
by a `nearby' or somehow related fact---that there are simples
arranged chairwise.

It should therefore seem reasonable to demand a similar explanation
from Unger.  This explanation would be expected to take a different
form, depending on whether it accompanies the sorites paradox or the
problem of the many.  However, Unger offers no explanations.  

\subsection{Explaining our beliefs given the sorites paradox}
\label{expl-sorites}
Unger claims that our belief that there are chairs, like our beliefs
that there are other ordinary things, are not justified, `nearly as
good as true', or even coherent.  Unger says that ``terms for ordinary
things are incoherent [and] cannot apply to anything real''
\citep[147]{unger1979}.

Unger should not deny that believe that there are ordinary things.  If
our beliefs about tables and chairs are invariably false (even
incoherent), then what causes us to form these beliefs?  Why do we
believe in ordinary things to begin with?

Unlike van Inwagen and Merricks, Unger does not offer an explanation.
Having denied the existence of all ordinary things, he makes no
attempt to explain why we have so many false beliefs or what gives the
impression of coherency to our use of them in communication.  He seems
almost to revel in the strangeness of his position:

\begin{squote}
Now, it must of course be admitted that these arguments undermine the
possibility of any endeavor I should try to propose, or even the
putative thought that I should propose anything, just as all of my
putative essay is undermined.  But even so, I shall (incoherently)
propose that what we have now to do is invent new expressions which
are not inconsistent ones, and by means of which we may, to some
significant extent, think coherently about concrete reality
(\citeyear[544]{unger1980b}).
\end{squote}

I do not have an argument against the proposition that nearly all of
our language is hopelessly incoherent.  I do have a very hard time
believing that this is true, however; I'm not sure Unger believes it
himself.

\subsection{Explaining beliefs given the problem of the many}
\label{expl-many}
When presenting the problem of the many, Unger declares that he
prefers to maintain that there are no chairs, rather than that there
are pluralities of chairs.  Having made this nihilistic claim,
however, he does not offer an explanation of why we do in fact believe
that there are chairs.  However, he does not deny (at least not
explicitly) that there are things arranged chairwise, so Merricks'
explanation (see section \ref{connection}) might serve for Unger too.
We might propose, on Unger's behalf, that we believe that there are
chairs because there are things arranged chairwise.

In this case, however, I am tempted to repeat my arguments against
Merricks (section \ref{dogbush}).  I claimed that if there are things
arranged chairwise, {\em then there are chairs}.  If our belief that
there are chairs is caused by things arranged chairwise, then it is a
true, not a false, belief.

If we reject Unger's conclusion that there are no chairs, we are still
faced with a problem.  For we seem to run ourselves into the other
disjunct of the problem of the many.  If there are chairs, then there
are pluralities of chairs where we expect there to be only one.

This is an unacceptable conclusion, but not due to any explanatory
deficiency.  If we supposed that there was a plurality of chairs, then
{\em that} would explain why we believe that there are chairs.

\section{Referring to the many}
\label{refer}
Above in section \ref{many-merricks} I mentioned that notions of
singular thought are threatened by the problem of the many.  If we
assume a plausible theory of referential communication, the problem of
the many seems to have the result that we cannot actually talk about
things like chairs and dogbushes.

The theory goes something like this: reference is a four-place
relation between a speaker, a term, a thing, and an audience.  (A
speaker might have more than one audience, so reference is {\em at
  least} a four-place relation.)  A speaker uses a term to refer her
audience to a thing.  Her {\em referential intention} is directed at
the thing; her audience is expected to recognize this intention.  If
the audience recognizes the speaker's referential intention, the
audience thereby recognizes which thing the speaker intends to refer
to.  The speaker and audience come to be thinking of the same thing;
thus reference {\em succeeds}.

Now suppose that the speaker says something like ``is that your
chair?''  She simultaneously points at a chair.  For her audience to
understand the question, the audience and the speaker must be thinking
of the same thing---the same chair.  But if we accept the conclusion
that Unger draws from the problem of the many, it seems to be the case
that, if there are any chairs where she pointed, there are {\em many}
chairs there.  Even if we suppose that the speaker's referential
intention is directed at a specific chair, the chance that the
audience can recognize the direction of this intention, and so come to
think of the same chair, is very low.  There is nothing in the
speaker's utterance or demonstration that could discriminate between
possibilities.  But if the speaker and audience are not thinking of
the same chair, then reference does not succeed, and the audience
cannot be said to understand the question.

This is an unacceptable result.  We obviously {\em do} engage in
successful referential communication with each other.  We must
therefore reject either the plausible theory of reference or one of
the premises that leads to the problem of the many.

\subsection{Indeterminacy and indecision}
The two most widely-held responses to the problem of the many (and the
sorites paradox) are epistimicism and supervaluationism.  Both rely on
the possibility of vague terms like `chair' being fully precise.  For
a term like `chair' to be fully precise would involve the term being
given exact boundary conditions, down to the atomic level (or lower).
If `chair' had this level of precision, it would avoid both the
sorites paradox and the problem of the many.  It would avoid the
sorites paradox by falsifying the second premise---there {\em would}
be an atom (or other thing) whose removal would destroy the chair.  It
would avoid the problem of the many by falsifying the premise that any
set of things `insignificantly different' from the set that composes
the chair would also compose a chair (there would be no such set).

These are both well-developed and interesting views, but both have
problems of their own.  Epistimicism seems implausible.
Supervaluationism relies on the premise that we are able to render all
vague terms precise, which may not be true.  In addition, both simply
seem to get things {\em backward}.  They seem to suppose that we must
determine a precise definition of `chair' {\em before} we can know
whether it is true or false whether a given utterance of ``that is a
chair'' is true.  But in almost every case, we {\em already} know
whether ``there is a chair'' is true.  Precisifying `chair' cannot
therefore {\em explain} why or show that ``there is a chair'' is true;
at best it can justify what we already know (that it is true or false,
as the case may be).

\subsection{Epistimicism}
Epistemicism involves the claim that the meanings of vague terms like
`heap' and `red' {\em are} precise, but that we do not (indeed,
cannot) know exactly what their boundary conditions are.  This is an
interesting view, but it seems very implausible that our (probably
inconsistent) use of vague terms determines their meaning with such
precision.  Peter Unger's judgement as to what is and is not absurd
may not be the most reliable, but I think he might be right here:

    \begin{squote}
      Does anyone imagine that our concept of a swizzle stick
      discriminates at the required atomic level?  Surely, this is
      quite absurd.  But, then, it is just as absurd in the case of
      tables, and of stones (\citeyear[126]{unger1979}).
    \end{squote}

\ldots

\subsection{Supervaluationism}
Supervaluationism requires the possibility of making vague terms
precise.  For example, `red' is a vague term.  Suppose we have a wall
of color swatches that shift from red to orange.  The difference in
color between two adjacent swatches is indiscriminable to the human
eye.  Nonetheless there are cases where it clearly is true to say
``that is red'', cases where it is clearly false, and intermediate
cases where it is unclear.  Supervaluationism proposes that a term
like `red' can be made precise in a number of different ways.  Each of
these `precisifications' will have the result that some of the
intermediate cases---when we are not sure if ``that is red'' is
true---will in fact be true, and others will be false.  Each
precisification leaves no cases indeterminate.  On each
precisification, therefore, there will be a sharp cut-off; one swatch
will be red and an adjacent swatch will not.  Each precisification
will, however, result in a different cut-off point.  For any swatch of
which it is true that ``that is red'' on one precisification and false
on another, it therefore remains indeterminate whether or not it is
red.  But for any swatch of which ``that is red'' is true on {\em all}
precisifications, it is true (or supertrue) that it is red.  Likewise
for swatches that are not red according to every precisification.

But there seem to be some vague terms that cannot admit of
precisification in this way.  It may be that a predicate like ``looks
as if it were red'' cannot be made precise.  Recall the series of
color swatches, moving indiscriminably from red to orange.  The
leftmost (red) patch certainly looks as if it were red, and the
rightmost (orange) patch certainly does not look as if it were red.
The supervaluationist method of precisification seems to demand that
we can make our predicate so precise as to have a sharp cut-off.  But
we stipulated that our series of color swatches are each of them
indistinguishable from their adjacent swatches.  So there {\em cannot}
be a sharp cut-off; for any swatch, if it looks red, its neighbors
will look red too.

\ldots

\subsection{Making a decision}
With these difficulties in mind, I'd like to sketch a different way of
looking at vague terms.  I will use as examples terms for ordinary
things like `chair'; I do not know if what follows will apply to all
vague terms.

One of the difficulties that the problem of the many presented for our
theory of communication was that it posits a huge number of candidates
for our referential intentions.  When I attempt to refer to a chair,
there are a plurality of chairs, each with slightly different
boundaries, at which I might be directing my referential intention.
Not only is my audience at a loss to recognize which chair I mean to
refer to, but how am {\em I} supposed to know?  If there really are an
absurdly large number of chairs (or at least `candidate' chairs),
there is no way I can direct my intention at one of these particular
chairs.  Referential intentions simply don't seem {\em fine-grained}
enough.  So not only does my audience not understand what I am talking
about, {\em neither do I}.

Neither epistimicism nor supervaluationism seems to help with this
problem.  Epistimicism has the result that I {\em cannot} know the
actual precisification of `chair'; so while I can know that I am
talking about a chair, there is a sense in which I can't think about
{\em the} chair.  I know there's {\em a} chair at which I am directing
my referential intention, but I there's a sense in which I don't have
a full grasp on it.  Supervaluationism seems no better.  For it admits
a huge (possibly infinite) number of precisifications for ``that is a
chair''.  Even if we suppose that ``that is a chair'' comes out true
on all precisifications, there is still a sense in which neither I nor
my audience know where the chair begins and ends.  In order to know
what I'm talking about, I should be able to know {\em exactly}.  (This
objection needs work; it might end up coming to nothing.)

So I want to deny both that there is a plurality of chairs (even chair
`candidates') and that I cannot know exactly what the object of my
referential intention is.  The way I hope to do this is as follows:

\begin{enumerate}
  \item When I say ``that is a chair'' (accompanied by the appropriate
    demonstration), it is either true or false.  If it is true, that
    is because there is a chair; it is false if there is not.  If
    there is a chair, my referential intention is directed at the
    chair.
  \item There are things we would obviously say are `parts' of the
    chair: the arms, the legs, the seat, the chairback.  When we
    direct our referential intention at the chair, our intention
    obviously includes these `parts' of the chair.
  \item There are other things we are less willing to say are `parts'
    of the chair.  These include the atoms (and other microscopic
    things) that are near where we would say the boundary of the chair
    is.
  \item When I say something like ``that is a chair'', for {\em every}
    atom that might be said to be part of the chair, it is
    indeterminate whether that atom is part of the chair.  For every
    possible boundary of the chair, it is indeterminate whether that
    is the boundary of the chair.
  \item If the question arises about one of these indeterminate
    aspects of the chair, then I must make a {\em decision}.  If my
    audience breaks some wood off the chair, puts it under a
    microscope and asks, ``was that molecule part of the chair?'' I
    then decide whether or not that molecule was part of what I
    referred to.
  \item It will be objected that what things are chairs becomes
    relative.  Chairs are supposed to be solid objects that exist
    whether or not we think they do; they have the parts they do
    regardless of what we think; how could we {\em decide} what is
    part of a chair?
  \item The motivation for this (admittedly bizarre) view is that
    chairs simply {\em don't} have fully determinate properties.
    Chairs are not like atoms.  We know perfectly well what it takes
    to be an atom, or at least physicists do.  Atoms can be described
    in precise detail.  Chairs just can't be described with similar
    precision.
  \item But even if someone were willing to grant that what it takes
    to be a chair is indeterminate, there is still an obvious
    objection.  Suppose we are in a room with one chair.  My audience
    asks me ``is that molecule part of the chair?'' and I say
    ``yes''.  My audience asks someone else, and they say ``no''.  How
    can I {\em decide} that the molecule in question is part of the
    chair while another person decides that it isn't?
  \item I think the only response I can make here is to restrict our
    respective decisions to the conversation in which they take
    place.  Thus, for the purposes of my conversation, the molecule
    was part of the chair, and for the purposes of the other
    conversation, it was not.  Absent such a conversational context,
    there is simply no fact of the matter as to whether that molecule
    is part of the chair.
  \item If within a conversation, I and my audience disagree over
    whether a molecule is part of the chair, then it is tempting to
    say that we have different chairs in mind.  But we agreed that
    there was only {\em one} chair in the room.  We may each conclude
    that the other is referring to the {\em wrong thing} with `chair'.
  %% \item I and the other person will both, of course, agree that there
  %%   is only one chair.  We will therefore assume that we are
  %%   disagreeing over the properties of that chair.

\end{enumerate}

\ifstandalone
\bibliography{everything}
\bibliographystyle{ChicagoReedweb}
\end{spacing}
\fi
\end{document}
